Linting Linearity in Core/System FC

### 2023-10-02 language-v4/proofs/optimizations/BetaReduction.tex
Apply Jacinta's corrections
+ optimiz -> optimis

\noindent Finally, $\beta$-reduction on multiplicity abstractions is also type
preserving. The argument of the application is a multiplicity rather than an
expression, so no resources are needed to type it, and since the body of the
lambda must treat the multiplicity $p$ as though it were a linear, the body
uses the argument linearly regardless of the instantiation of $p$ at $\pi$.

>>>>

\noindent Finally, $\beta$-reduction on multiplicity abstractions is also type
preserving. The argument of the application is a multiplicity rather than an
expression, so no resources are needed to type it, and, since the body of the
lambda must treat the multiplicity $p$ as though it were linear, the body uses
the argument linearly regardless of the instantiation of $p$ at $\pi$.
